---
title: "Introduce mixmodcluster package"
author: "Thi Ha Anh NGUYEN, Pape DIOUF"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduce mixmodcluster package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The mixmodcluster package contains 2 types of function:

- The first one is function clustermixmod(). This function is used to fit mixture models of a given quantitative,qualitative or heterogeneous data. For quantitative data (which the parameter of function: datatype = "continuous"), we use Gaussian mixture model(GMM). For qualitative data(which the parameter of function: datatype = "categorical"), we use Latent class model(LCM). For heterogeneous data, we use mixture model of Gaussian and Latent class model.

- The second consists 3 plot functions which correspond to 3 types of model. For quantitative data (GMM), we use function plot_continuous(). For qualitative data(LCM), we use function plot_categorical(). For heterogeneous data, we use function plot_mix().

## Example

```{r, fig.show='hold'}
library(mixmodcluster)
library(bayess)
library(mvtnorm)

# Data quantitative
x1 = as.matrix(iris[, 1:4])
# Fit model 
model1 = clustermixmod(x1, 2, itermax = 30, init = "kmeans", datatype = "continuous")
# Plot the result
plot_continuous(x1, model1)
```

